The Feasibility of Stylometry as a Service

### 2013-12-11 paper/paper.tex
Added figures and some more text.

The architecture of Anonymouth is that of a conventional desktop
application.  It uses a layered architecture with essentially two main
components: the frontend Graphical User Interface (GUI) and the
backend, consisting of the Weka machine learning toolkit and Jstylo.
Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
designed as a monolithic application, there are direct dependencies
between the layers without the use of an adaptation layer.

@@

@@

Besides multi-authors, the service is also multi-user.

@@

@@

\section{Security Analysis}

@@

{\bf Man in the middle attacks}: If a user accepts a rogue SSL certificate, it
may be possible to create a "man in the middle" attack where the user
believes he/she is communicating with a specific Stylometry Service,
but is infact communicating via an impersonated target.

{\bf Replay attacks}: An evesdropper may 'replay' a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented \cite{BrowserTiming} whereby Firefox optimizations
in the implementation of the requestAnimationFrame method have been
used by to detect differences in link coloring across frames (allowing
an adversary to determine if a particular styometry service has been
visited, for instance)

@@

We implemented a web application based on the Play Web Application
Framework in Java. This web application had a reference to a modified
version of JSAN which was forked from the PSAL Anonymouth repository
(https://github.com/psal/anonymouth) on September 29, 2013. In
addition the application has major dependencies on JQuery, Twitter
Bootstrap (for page layout), and Etherpad  (an open-source collaborative text editing
web application and library). Etherpad (specifically Etherpad Lite is
the version used here) in turn has major dependencies on
node.js for building and running the backend service.

At a high level the implementation is as follows: A user browses to
the Stylometry Service via a web browser. This causes the Play
Framework web application to serve up a web page with an Etherpad control
and instructions for the user to enter in the document they wish to
anonymize. The etherpad control is implemented as an iframe which
serves an Etherpad that is connected to the node.js server running the
Etherpad backend (both servers should reside on the same domain,
running on different ports). The page served by Play also contains a
button which allows the author to specify when he or she would like to
submit the document for anonymization to Anonymouth. Because the
Anonymouth analysis process depends on a number of
computationally-intensive algorithms (among them running SMO analysis
in Weka as well as a Basic-9 feature stylometric analysis) we
implemented this calculation asynchronously. When a user clicks the
button to run an analysis, JQuery is used to issue a HTTP POST
containing in the message body a JSON-encoded
representation of the current Etherpad text to an endpoint at
/getAnonymouthInfoJSON. During the time that the Anonymouth analysis
is underway, a spinner control from the spin.js library is used to
indicate to the user than an analysis is underway. The fact that the
request is made to Anonymouth asynchronously allows a user to continue
editing the text while an analysis is running, allowing for a smooth
user experience.

The web service as implemented currently supports only 1 author as the assumption is
made that the author has pre-configured the "doc set" (also referred
to as 'problem set' in Anonymouth source) that provides references as
to the author's own writing style, as well as writing samples for
other authors that will be used as a reference for writing styles that
are different than that of the active author. The user can
additionally configure the anonymouth properties file
(anonymouthprop.prop) in the jsan resources directory to influence
settings such as the feature set to use for stylometric identification
as well as the number of threads to use and maximum number of features
to analyze.

One configured, the call to the getAnonymouthInfoJSON input will
overwrite the "test.txt" file on disk that is configured in the provided problem
set. This will ensure that changing the document in Etherpad forces an
update to the test file and thus ensuring that the 'latest' document
is always anonymized. Once the problem set has been updated, the
'Anonymouth library' is invoked. The 'Anonymouth library' is a forked
version of the current Anonymouth application, which is designed to be
used behind a Swing/AWT rich client GUI. A number of implementation
challenges were present when trying to separate the core anonymization
logic of Anonymouth from its GUI implementation - most specifically,
although an 'engine' namespace exists which holds much of the
anonymization logic, significant dependencies still existed between
the 'engine' and the 'GUI' namespaces, specifically in the event
handlers associated with the Editor screen and the GUIMain classes. Much of the work in this
project consisted of reducing the coupling between these two
namespaces.

As much of the configuration logic was handled at the GUI layer (via
ThePresident and GUIMain classes) we took the approach of refactoring
the GUI layer to work in a 'headless' mode, that is, without any
windows launching. Long-term it would be preferable to have no
dependencies on the GUI namespace at all for the Stylometry Service,
however this could not be achieved in the available timeframe for this
project. The web service thus invokes a modified version of the
ThePresident class, which coordinates reading configuration files,
loading the configured problem set, and using numerous libraries
(JGAAP and Weka among them) to conduct an adversarial stylometric
analysis. The results are returned by the web service in the form of a
JSON-encoded list of words to remove, as well as an indication of
'changes needed' to the current text to reach an acceptable level of
anonynmity.

@@

The web application (bundled with all dependencies) can be downloaded
by cloning https://github.com/LRParser/anonymouth and running the
following command:

./bootstrap.sh

This command will copy the latest JSAN JAR files to the 'lib'
directory of the Play Framework Web Application, start a Play
Framework Server on port 9000, and start an Etherpad Lite server on
port 9001 over node.js.

@@

The web application can be deployed via the following commands on a
Ubuntu 12.04 desktop installation:

@@

The responses of users on Mechanical Turk (who were trying to
anonymize a text without any supporting software) were compared with
anonymization attempts by the authors of this paper against the same
document. The anonymization attempts by the authors took place before
reviewing the submissions from Mechanical Turk. For one sample paper,
d 09.txt from the Brennan-Greenstadt corpus (Michael Brennan and Rachel Greenstadt. Practical Attacks Against Authorship Recognition Techniques in Proceedings of the Twenty-First Conference on Innovative Applications of Artificial Intelligence (IAAI), Pasadena, California, July 2009.
), we noted that Anonymouth returned a "changes needed" score
on the original document of 2.518, 2.677 for the users 'naive' attempt
to anonymize over Mechanical Turk, and 2.467 for the attempt of one of
the authors to anonymize using the web application created in this
paper. Each of the two anonymization attempts for the 500-word
document took approximately 15 minutes. Although these results are far from achieving statistical
significance, they do suggest that it may be possible to use this
software to achieve anonymization levels which surpass those of a
'naive' anonymization attempt.

>>>>

The architecture of Anonymouth is that of a conventional desktop
application.  It uses a layered architecture with essentially two main
components: the frontend Graphical User Interface (GUI) and the
backend, consisting of the Weka machine learning toolkit and Jstylo.
Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
designed as a monolithic application, there are direct dependencies
between the layers without the use of an adaptation layer.  Figure
\ref{fig:jsan} illustrates the architecture in a layered drawing.  In
this drawing, components, represented as boxes, can call software
below and to the right.

@@

\begin{figure}
  \centering
    \includegraphics[width=0.4\textwidth]{img/jsan.pdf}
  \caption{Existing JSAN Architecture}
  \label{fig:jsan}
\end{figure}

@@

Besides multi-authors, the service is also multi-user.  Thus, the
user's document is loaded into RAM with other user's documents.
Therefore, the service is vulnerable to memory dump attacks.  Assuming
that the service runs on a third party provide, like Amazon Web
Services, it is also vulnerable to malicious insiders
\cite{conf/dsn/RochaC11}.

{\bf Integrity.}  The service must maintain the integrity of the
corpus and the target document.  This not only includes integrity in
transit but also the integrity of the presented document to the user.
Using Transport Layer Security (TLS), the integrity is guaranteed
during transit.

{\bf Repudiation.}  The service must not assign long-term identity
to any operations.  Therefore, TLS connections must use ephemeral
keys to provide Perfect Forward Secrecy (PFS).  The service must not
maintain logs that will identify the target document, the corpus, or
the users of the service.

@@

The service must be modular in design to support testing of each
endpoint.  While adopting the full Netflix-like approach may be
over-engineering for this limited web-service,
\cite{Tseitlin:2013:AO:2492007.2492022}, there are certainly aspects
of their design that are applicable.  For example the service should
be resilient to service outages.  If the service is unavailable, it
can not protect the anonymity of authors.

@@

\subsection{Example Architecture}

\begin{figure*}
  \centering
    \includegraphics[width=0.6\textwidth]{img/jsanaas.pdf}
  \caption{Example JSANaaS Architecture as a Deployment Diagram}
  \label{fig:jsanaas}
\end{figure*}
\section{Security Analysis}

@@

{\bf Man in the middle attacks}: If a user accepts a rogue SSL
certificate, it may be possible to create a "man in the middle" attack
where the user believes she is communicating with a specific
Stylometry Service, but is infact communicating via an impersonated
target.

{\bf Replay attacks}: An evesdropper may replay a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented \cite{BrowserTiming} whereby Firefox optimizations
in the implementation of the requestAnimationFrame method have been
used by to detect differences in link coloring across frames (allowing
an adversary to determine if a particular styometry service has been
visited, for instance).

@@

We implemented a web application based on the Play Web Application
Framework in Java. This web application had a reference to a modified
version of JSAN which was forked from the PSAL Anonymouth repository
\cite{PSAL:github}. In addition the application has major dependencies
on JQuery, Twitter Bootstrap (for page layout), and Etherpad (an
open-source collaborative text editing web application and library)
\cite{etherpad}. Etherpad (specifically Etherpad Lite is the version
used here) in turn has major dependencies on node.js for building and
running the backend service.

At a high level the implementation is as follows: A user browses to
the Stylometry Service via a web browser. This causes the Play
Framework web application to serve up a web page with an Etherpad
control and instructions for the user to enter in the document they
wish to anonymize. The etherpad control is implemented as an iframe
which serves an Etherpad that is connected to the node.js server
running the Etherpad backend (both servers should reside on the same
domain, running on different ports). The page served by Play also
contains a button which allows the author to specify when he or she
would like to submit the document for anonymization to
Anonymouth. Because the Anonymouth analysis process depends on a
number of computationally-intensive algorithms (among them running SMO
analysis in Weka as well as a Basic-9 feature stylometric analysis) we
implemented this calculation asynchronously. When a user clicks the
button to run an analysis, JQuery is used to issue a HTTP POST
containing in the message body a JSON-encoded representation of the
current Etherpad text to an endpoint at
\url{/getAnonymouthInfoJSON}. During the time that the Anonymouth
analysis is underway, a spinner control from the spin.js library is
used to indicate to the user than an analysis is underway. The fact
that the request is made to Anonymouth asynchronously allows a user to
continue editing the text while an analysis is running, allowing for a
smooth user experience.

The web service as implemented currently supports only 1 author as the
assumption is made that the author has pre-configured the "doc set"
(also referred to as 'problem set' in Anonymouth source) that provides
references as to the author's own writing style, as well as writing
samples for other authors that will be used as a reference for writing
styles that are different than that of the active author. The user can
additionally configure the anonymouth properties file
(\texttt{anonymouthprop.prop}) in the jsan resources directory to influence
settings such as the feature set to use for stylometric identification
as well as the number of threads to use and maximum number of features
to analyze.

One configured, the call to the \texttt{getAnonymouthInfoJSON} input
will overwrite the "test.txt" file on disk that is configured in the
provided problem set. This will ensure that changing the document in
Etherpad forces an update to the test file and thus ensuring that the
'latest' document is always anonymized. Once the problem set has been
updated, the 'Anonymouth library' is invoked. The 'Anonymouth library'
is a forked version of the current Anonymouth application, which is
designed to be used behind a Swing/AWT rich client GUI. A number of
implementation challenges were present when trying to separate the
core anonymization logic of Anonymouth from its GUI implementation -
most specifically, although an 'engine' namespace exists which holds
much of the anonymization logic, significant dependencies still
existed between the 'engine' and the 'GUI' namespaces, specifically in
the event handlers associated with the Editor screen and the
\texttt{GUIMain} classes. Much of the work in this project consisted
of reducing the coupling between these two namespaces.

As much of the configuration logic was handled at the GUI layer (via
\texttt{ThePresident} and \texttt{GUIMain} classes) we took the
approach of refactoring the GUI layer to work in a 'headless' mode,
that is, without any windows launching. Long-term it would be
preferable to have no dependencies on the GUI namespace at all for the
Stylometry Service, however this could not be achieved in the
available timeframe for this project. The web service thus invokes a
modified version of the \texttt{ThePresident} class, which coordinates
reading configuration files, loading the configured problem set, and
using numerous libraries (JGAAP and Weka among them) to conduct an
adversarial stylometric analysis. The results are returned by the web
service in the form of a JSON-encoded list of words to remove, as well
as an indication of 'changes needed' to the current text to reach an
acceptable level of anonynmity.

@@

The web application (bundled with all dependencies) can be downloaded
as shown in Listing \ref{lst:download}.

\begin{lstlisting}[caption={Download Web Application},label={lst:download}]
git clone https://github.com/LRParser/anonymouth.git
./bootstrap.sh
\end{lstlisting}

This command will copy the latest JSAN JAR files to the \texttt{lib}
directory of the Play Framework Web Application, start a Play
Framework Server on port $9000$, and start an Etherpad Lite server on
port $9001$ over node.js.

@@

The web application can be deployed on a Ubuntu 12.04 desktop
installation per Listings \ref{lst:install} and \ref{lst:start}.

@@

The responses of users on Mechanical Turk (who were trying to
anonymize a text without any supporting software) were compared with
anonymization attempts by the authors of this paper against the same
document. The anonymization attempts by the authors took place before
reviewing the submissions from Mechanical Turk. For one sample paper,
d \texttt{09.txt} from the Brennan-Greenstadt corpus \cite{BrennanG09}
, we noted that Anonymouth returned a "changes needed"
score on the original document of $2.518$, $2.677$ for the users 'naive'
attempt to anonymize over Mechanical Turk, and $2.467$ for the attempt
of one of the authors to anonymize using the web application created
in this paper. Each of the two anonymization attempts for the 500-word
document took approximately 15 minutes. Although these results are far
from achieving statistical significance, they do suggest that it may
be possible to use this software to achieve anonymization levels which
surpass those of a 'naive' anonymization attempt.
